---
title: "Syllabus"
slug: syllabus
date: '`r Sys.Date()`'
citeproc: yes
output:
  html_document:
    toc: yes
    df_print: paged
  blogdown::html_page:
    toc: yes
    fig_caption: no
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
```
# Diversity and Inclusion In Class

> I would like to create a learning environment for my students that supports a diversity of thoughts, perspectives and experiences, and honors your identities (including race, gender, class, sexuality, religion, ability, SES, etc.  )To help accomplish this:

> - If  you  have  a  name  and/or  set  of  pronouns  that  differ  from  those  that  appear  in  your  official  Princeton records, please let me know!

> - If you feel like your performance in the class is being impacted by your experiences outside of class or in class,  please bon’t hesitate to come and talk with me. I want to be a resource for you. Remember that you can also submit anonymous feedback (which will lead to me making a general announcement to the class, if necessary to address your concerns).

> - I (like many people) am still in the process of learning about diverse perspectives and identities.  If something was said in class (by anyone) that made you feel uncomfortable, please talk to me about it.  (Again,anonymous feedback is always an option). 

# Course Introduction

Research methodology/design, measurement, statistical analysis, and statistical computing are vast areas, each with their own texts, literature, advances, and sub-disciplines within psychology. Exhaustive coverage of any one of these topics is beyond the scope of a semester-long course. Rather, my goal is to provide you with a solid introduction to these topics and to develop an understanding of how integration of these areas is vital to conducting scientific research. My hope is that this course prepares you to pursue further coursework and independent study in each of these quantitative areas.


\vspace{.75cm}
# Topics

This course covers the statistical and computational foundations of psychological methods. You will learn about probability theory, causal inference, statistical inference, and the general linear model. 

We will use R, R Markdown, and Git/GitHub.

\vspace{.75cm}
# Audience

This course is designed for quantitative psychologists but it is relevant to any social and natural scientists studying human behavior.  

\vspace{.75cm}
# Prerequisite

The main prerequisite for this course is a strong desire and willingness to learn. It is not essential that you have taken any statistics, probability, or programming courses in the past. We will start with the basics.   

__NOTE:__ Students are expected to enroll in _PSY 505: Advances in Statistical Methods and Research Practices in Psychology_ (Fall 2022, T: 11am - 1pm), which constitutes an important complement to this course. You can think of PSY 505 as the required precept time of the week for PSY 503. Please reach out to me if you would like to enroll in PSY 503 but are not able to take PSY 505.      

\vspace{.75cm}

# Course Objectives

-	Apply principles of causal inference
- Understand principles of probability and likelihood
-	Understand statistical inference in classical frameworks
-	Build and interpret general linear models
-	Diagnose model misspecification and misfit
-	Use statistical models to inform decisions, make predictions, and answer scientific questions
-	Implement statistical models in a modern computing environment

# Student Learning Outcomes

At the end of the course, students will be able to:

-	Interpret probabilities, confidence intervals, p values, and likelihood, posterior, and confidence distributions
-	Fit general models in R
-	Create informative visualizations of data, model predictions, and model diagnostics
-	Interpret standardized and unstandardized effect sizes from general linear models 
-	Express conclusions drawn from generalized linear models in terms of estimates and uncertainty
-	Translate numerical model results into implications for scientific questions
-	Use analytic and simulation methods to make predictions from generalized linear models
-	Diagnose and correct model misfit in generalized linear models
-	Apply course principles and skills to basic multilevel models
-	Prepare analytic reports using RMarkdown

# Office Hours

I will hold weekly office hours (M: 1-3 P.M.; W: 1-2 P.M.) If you need to see me outside of these hours please schedule using the link on the website. 

# Textbooks

No textbook is required for this course. 

I am going to use a combination of articles and textbook chaI will post links to all readings on the course website. 

# Absences and Late Work

If you need to be absent or submit an assignment late, please let me and Alex know as soon as possible. We don’t need to know your personal or medical details. We can be flexible, but please respect my and Alex’s time by turning your assignments in on time whenever possible.

\vspace{.75cm}
# Assignments

## Problem Sets

```{r, child="/Users/jgeller1/Desktop/psy503-stats-princeton/static/content/DDA.Rmd"}

```

## Final Project

```{r, child="/Users/jgeller1/Desktop/psy503-stats-princeton/static/content/Project.Rmd"}

```

## Final Exam

The final exam will be take-home and will involve analyzing and interpreting several datasets. 


## Participation

It is important that you engage with the material. To this end, It is expected you will participate during class (i.e., come prepared each class session with questions and comments). To make sure you understand the material, and are engaging with it, I will frequently quiz you before class. These quizzes will part of your participation grade.  


# Grades

```{r assignments-grades, include=FALSE}
assignments <- tribble(
  ~Points,  ~Assignment, 
  10*5      , "Problem Sets",
  20, "Final Project",
  20, "Final Exam", 
    10, "Participation"
) %>%
  mutate(Percent = Points / sum(Points),
         Percent = scales::percent(Percent)) 

grading <- tribble(
  ~Grade, ~Range,
  "A",  "90–100%",
  "B",  "80–89%",
   "C",  "70-79%", 
  "D",  "60-69%"
)
```

```{r show-assignments-table, echo=FALSE, results="asis"}
assignments_total <- tibble(Assignment = "Total",
                            Points = sum(assignments$Points),
                            Percent = NA)

bind_rows(assignments, assignments_total) %>% 
  select(Assignment, Percent, Points) %>% 
  pandoc.table(justify = "lrr", missing = "")
```


```{r show-grades-table, echo=FALSE, results="asis"}
grading %>%
  pandoc.table(justify = "lc", 
               col.names = c("Grade", "Range"))
```


